### 2023-08-22 state-resilience.tex
up

Resilience is a strong property that implies that from every element of $\Bad$ there must exist a path to $\Safe$. However, when one considers a system with an initial state $s_0$, it could be sufficient to only ask that from $\Bad \cap \post^*(s_0)$, there must exist a path to $\Safe$. 
In the {\bf Flight Controller System}, the state $(q_{A,1}, q_{M,4}, q_{B,0})(\textbf{0})$
belongs to $\Bad$, but is not reachable from $(q_{A,0}, q_{M,0}, q_{B,0})(\textbf{0})$,
hence it may seem unnecessary to check for the existence of a path to $\Safe$ from this element.
Since we still consider $\Bad$ and $\Safe$ complements of each others, this is akin to asking whether from $\post^*(s_0)$ there always exists a path to $\Safe$. 
The three previous problems become:

@@

We start with the case $\Safe = \uparrow \Safe$ hence $\Bad = \downarrow \Bad$.
%
Unfortunately, in this case {\sc State-resilience} is undecidable for (general) WSTS even with strong upward-compatibility.
This stems from the fact that it is undecidable in the particular case of reset-VASS,
where  $t$-liveness is both undecidable and 
 reducible to {\sc State-resilience}. This undecidability result furthermore implies the undecidability of the other two state resilience problems by straightforward reductions.

@@

However when removing strong compatibility, precision is lost.
Since $\pred(\uparrow \Safe)$ is not necessarily upward-closed, it is possible to have 
 $\uparrow \post^* (s) \cap S \not\subseteq \pred(\Safe)$,
despite having 
$\post^* (s) \cap S \subseteq \pred( \Safe)$.
In such a case the algorithm from
\cite{DBLP:conf/gg/Ozkan22} would deduce that $1$-rechable-resilience does not hold,
which is incorrect.

@@

We now consider the case $\Safe = \downarrow \Safe$ hence $\Bad = \uparrow \Bad$.
%
Unfortunately the {\sc State-resilience} problem is undecidable for WSTS in the case $\Safe = \downarrow \Safe$. As for resilience in WSTS when $\Safe = \downarrow \Safe$, it stems from undeciability of the corresponding problem in Minsky machines, the executions of which can be simulated by reset-VASS, as seen in % Appendix~\ref{HS-Minsk}.

>>>>

Resilience is a strong property that implies that from every element %of $\Bad$
 there must exist a path to $\Safe$. However, when one considers a system with an initial state $s_0$, it could be sufficient to only ask that from 
 $
 % \Bad \cap 
 \post^*(s_0)$, there must exist a path to $\Safe$. 
%In the {\bf Flight Controller System}, the state $(q_{A,1}, q_{M,4}, q_{B,0})(\textbf{0})$ belongs to $\Bad$, but is not reachable from $(q_{A,0}, q_{M,0}, q_{B,0})(\textbf{0})$, hence it may seem unnecessary to check for the existence of a path to $\Safe$ from this element.
%
% Since we still consider $\Bad$ and $\Safe$ complements of each others, this is akin to asking whether from $\post^*(s_0)$ there always exists a path to $\Safe$. 
The three previous problems become:

@@

We start with the case $\Safe = \uparrow \Safe$.
%
Unfortunately, in this case {\sc State-resilience} is undecidable for (general) WSTS even with strong upward-compatibility.
This stems from the fact that it is undecidable in the particular case of reset-VASS,
where  $t$-liveness is both undecidable and 
 reducible to {\sc State-resilience}. This undecidability result furthermore implies the undecidability of the other two state resilience problems by straightforward reductions.

@@

However when removing strong compatibility, precision is lost.
Since $\pred(\uparrow \Safe)$ is not necessarily upward-closed, it is possible to have 
 $\uparrow \post^* (s) \cap S \not\subseteq \pred(\Safe)$,
despite having 
$\post^* (s) \cap S \subseteq \pred( \Safe)$.
In such a case the algorithm from
\cite{DBLP:conf/gg/Ozkan22} would deduce that {\sc $1$-state-resilience} does not hold,
which is incorrect.

@@

We now consider the case $\Safe = \downarrow \Safe$.
%
Unfortunately the {\sc State-resilience} problem is undecidable for WSTS in the case $\Safe = \downarrow \Safe$. As for resilience in WSTS when $\Safe = \downarrow \Safe$, it stems from undeciability of the corresponding problem in Minsky machines, the executions of which can be simulated by reset-VASS, as seen in 
% Appendix~\ref{HS-Minsk}. 
Section~\ref{safe-down}.
